Hybrid Threads for the Parrot Virtual Machine

### 2012-02-25 Paper.tex
Scheduler PMC

@@

@@

\section{The Scheduler (4)}

The scheduler is the place where most of the green thread logic is implemented. It's functions use the prefix \textit{Parrot\_cx} and are located in \textit{src/scheduler.c}.

@@

>>>>

This chapter is talking about programming platforms. A platform is seen as a combination of a programming language and a runtime. For example for the Python programming language there are multiple runtimes with different implementations of threading support.

@@

PMCs are implemented in .pmc files with method bodies written in C. These files get preprocessed to plain C before compliation.

@@

\section{The Scheduler (3)}

The scheduler is the place where most of the green thread logic is implemented. It consists of two parts: functions using the prefix \textit{Parrot\_cx} which are located in \textit{src/scheduler.c} and the scheduler PMC type containing the scheduler's data and public interface.

@@

\section{Scheduler PMC (1)}

The scheduler PMC contains the following attributes:
%
\begin{itemize}
\item PMC *task\_queue: List of tasks/green threads waiting to run
\item Parrot\_mutex task\_queue\_lock: a lock protecting the task\_queue so other threads might access it safely
\item PMC *alarms: List of future alarms ordered by time
\item PMC *all\_tasks: Hash of all active tasks by ID
\item UINTVAL next\_task\_id: ID to assign to the next created task
\item Parrot\_Interp interp: A reference to the scheduler's interpreter.
\end{itemize}

\textit{push\_pmc} and \textit{unshift\_pmc} are used to add a task at the end respectively the beginning of the task\_queue. \textit{shift\_pmc} is used to fetch and remove a task from the tip of the task\_queue. \textit{get\_integer} returns the number of tasks in the task\_queue. These four methods use the task\_queue\_lock to make accessing the task\_queue thread safe.

\textit{alarms} is list containing all pending alarms, sorted by their expiry time. Sorted insertion is used to keep alarms in order. Sorting makes it simple and efficient to retrieve all alarms that have expired at a certain point in time.

The textit{active\_tasks} returns an array containing all tasks which have been run at least once and are not yet finished, e.g. they are currently being executed or are preempted.

\section{Task PMC}
